---
title: "ice cream and frog data"
author: WEI, LIANG YU
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ice Cream
#### DATA
```{r}
data<-read.csv("final.csv",header=T)
y<-data[,2]
A<-factor(data[,3]) #Time 
B<-factor(data[,4]) #Milk Type
block<-factor(data[,5]) #user
data
```

#### BOX PLOT
```{r}
par(mfrow=c(2,2))
plot(A,y,xlab="Time",ylab="ML") #Time
plot(B,y,xlab="Type",ylab="ML") #Milk Type
plot(block,y,xlab="Block(user 1 and user 2)",ylab="ICE") #user 1 and 2
par(mfrow=c(1,1))
```

#### QQPLOT
```{r}
par(mfrow=c(2,2))
plot(as.numeric(A),y,xlab="Time",ylab="ICE")
plot(as.numeric(B),y,xlab="Water",ylab="ICE")
plot(as.numeric(block),y,xlab="Block(user 1 and user 2)",ylab="ICE")
par(mfrow=c(1,1))
```

#### ANOVA analysis
```{r}
rlt<-aov(y~A*B+block)
summary(rlt)
```
ALL P-Value > 0.05, thus these factor is nonsignificant.

#### Residual Plot
```{r}
e<-rlt$residuals
y.hat<-rlt$fitted.values
ord<-data[,1]

par(mfrow=c(2,2))

plot(ord,e,xlab="Run order",ylab="eij",main = "Independency" )
abline(0,0)

plot(y.hat,e,xlab="y.hat",ylab="eij" , main = "Constant Variance")
abline(0,0)

qqnorm(e)

par(mfrow=c(1,1))

```
The points are not uniformly distributed at 0, so Non-Constant Variance.
 
#### shapiro test
```{r}
shapiro.test(e)
```

# Frog

#### Data
```{r}
data<-read.csv("frog.csv",header=T)

y<-data[,2]
A<-factor(data[,3]) #number of pin
B<-factor(data[,4]) #Type(Big and Small)
C<-factor(data[,5]) #Fold
data
```

#### Frog BOX PLOT
```{r}
par(mfrow=c(2,2))
plot(A,y,xlab="Number of Pin",ylab="distance")
plot(B,y,xlab="Type(Big and Small)",ylab="distance") # type1: small frog, type2: big frog
plot(C,y,xlab="Fold",ylab="distance")
par(mfrow=c(1,1))
```

#### Frog QQ PLOT
```{r}
par(mfrow=c(2,2))
plot(as.numeric(A),y,xlab="Number of Pin",ylab="distance")
plot(as.numeric(B),y,xlab="Type(Big and Small)",ylab="distance")
plot(as.numeric(C),y,xlab="Fold",ylab="distance")
par(mfrow=c(1,1))
```

#### ANOVA analysis
```{r}
rlt<-aov(y~A*B*C)
summary(rlt)
```
The P-value of factor B(frog size), interaction AB, interaction AC and interaction BC is smaller than 0.05. 
That means these factor are nonsignificant.

#### PLOT
```{r}
par(mfrow=c(2,3))

Ai.bar<-tapply(y,A,mean)
plot(names(Ai.bar),Ai.bar,type="b",xlab="A",ylab="Average y",ylim=c(10,25))

Bi.bar<-tapply(y,B,mean)
plot(names(Bi.bar),Bi.bar,type="b",xlab="B",ylab="Average y",ylim=c(10,25))

Ci.bar<-tapply(y,C,mean)
plot(names(Ci.bar),Ci.bar,type="b",xlab="C",ylab="Average y",ylim=c(10,25))

interaction.plot(A,B,y,xlab="A",ylab="Average y",ylim=c(5,30))
interaction.plot(A,C,y,xlab="A",ylab="Average y",ylim=c(5,30))
interaction.plot(B,C,y,xlab="B",ylab="Average y",ylim=c(5,30))

par(mfrow=c(1,1))
```
The degree of influence of each factor is A>B>C.

#### Residual PLOT
```{r}
e<-rlt$residuals
y.hat<-rlt$fitted.values
ord<-data[,1]

par(mfrow=c(2,2))

plot(ord,e,xlab="Run order",ylab="eij",main = "Independency")
abline(0,0)

plot(y.hat,e,xlab="y.hat",ylab="eij", main = "Constant Variance")
abline(0,0)

qqnorm(e)


par(mfrow=c(1,1))
```

#### shapiro test
```{r}
shapiro.test(e)
```
### Delete the factor B(frog size), interaction AB, interaction AC and interaction BC.
#### (After) ANOVA analysis
```{r}
rlt.1<-aov(y~A+C)
summary(rlt.1)
```

#### (After) Residual PLOT
```{r}
e<-rlt.1$residuals
y.hat<-rlt.1$fitted.values
ord<-data[,1]

par(mfrow=c(2,2))

plot(ord,e,xlab="Run order",ylab="eij",main = "Independency")
abline(0,0)

plot(y.hat,e,xlab="y.hat",ylab="eij", main = "Constant Variance")
abline(0,0)

qqnorm(e)

par(mfrow=c(1,1))
```

#### (After) shapiro test
```{r}
shapiro.test(e)
```

### Conclusion
```{r}
cbind(A,B,C,y.hat)
```
The big frog with one fold and small frog with one fold are the farthest.

```{r pressure, echo=FALSE}
```